Cancer Applications of Choropleth Maps, and the Potential of Cartograms and Alternative Map Displays

### 2019-12-16 review_article.Rmd
di meeting changes

---
title: "Cancer Applications of Choropleth maps, and the Potential of Cartograms and Alternative Map Displays"
author: "Stephanie Kobakian, Jessie Roberts and Dianne Cook"
bibliography: reviewbib.bib
output:
  pdf_document:
    fig_caption: yes
    number_sections: yes
    toc: no
    toc_depth: 3
  word_document:
    toc: no
    toc_depth: '3'
link-citations: yes
fontsize: 11pt
csl: springer-vancouver.csl
yolo: yes
---

@@

# Traditional approaches for cancer map displays {#ch:choropleth maps}
<!-- 381 words -->
<!-- what is a choropleth map -->
A choropleth map displays the geographical distribution of data over a set of spatial units by shading areas of a map [@EI, @BCM]. Faithful rendering of the geography, when combined with an appropriate color scheme, can reveal spatial patterns among data values. Identifying and explaining spatial structures, patterns, and processes involve considering the individuals and organizing them into representable units of communities [@SAMGIS]. Early versions of choropleth maps used symbols or patterns instead of color. Choropleth maps can be used for displaying disease data [@DMAHP], including cancer data [@CPISACA]. In epidemiology, choropleth maps are often used as a tool to study the spatial distribution of cancer incidence and mortality.

@@

```{r choropleth-grid-create, message=FALSE, warning = FALSE, fig.cap = "Examples of publicly available choropleth cancer maps.", out.width='100%', fig.align='center', fig.width=12, fig.height=10}
library(cowplot)

@@

## Additional materials
<!-- 479 words -->
Cancer atlases often display supplementary graphs and plots to add more information. Additional materials such as tables, graphs, and text explanations support understanding and inference derived from maps, ensuring the message communicated will be consistent across a range of viewers [@CPISACA]. The many displays of statistical summaries, including dot plots, bar plots, box plots, cumulative distribution plots, scatter plots, and normal probability plots, can provide alternative views of the cancer statistics. These can also display supporting statistics such as error, confidence intervals, distributions, sample or population sizes, and standard deviation.

>>>>

---
title: "Cancer Applications of Choropleth Maps, and the Potential of Cartograms and Alternative Map Displays"
author: "Stephanie Kobakian, Jessie Roberts and Dianne Cook"
bibliography: reviewbib.bib
output:
  pdf_document:
    fig_caption: yes
    number_sections: yes
    toc: no
    toc_depth: 3
  word_document:
    toc: no
    toc_depth: '3'
link-citations: yes
fontsize: 11pt
csl: springer-vancouver.csl
yolo: yes
---

@@

# Traditional approaches for cancer map displays {#ch:choropleth_maps}
<!-- 381 words -->
<!-- what is a choropleth map -->
A choropleth map displays the geographical distribution of data over a set of spatial units by shading areas of a map [@EI, @BCM]. Faithful rendering of the geography, when combined with an appropriate color scheme, can reveal spatial patterns among data values. Identifying and explaining spatial structures, patterns, and processes involve considering the individuals and organizing them into representable units of communities [@SAMGIS]. Early versions of choropleth maps used symbols or patterns instead of color. Choropleth maps can be used for displaying disease data [@DMAHP], including cancer data [@CPISACA]. In epidemiology, choropleth maps are often used as a tool to study the spatial distribution of cancer incidence and mortality.

@@

```{r choropleth-grid-create, message=FALSE, warning = FALSE, fig.cap = "A selection of choropleth cancer maps available online.", out.width='100%', fig.align='center', fig.width=12, fig.height=10}
library(cowplot)

@@

## Additional considerations
<!-- 479 words -->
Cancer atlases often display supplementary graphs and plots to add more information. Additional materials such as tables, graphs, and text explanations support understanding and inference derived from maps, ensuring the message communicated will be consistent across a range of viewers [@CPISACA]. The many displays of statistical summaries, including dot plots, bar plots, box plots, cumulative distribution plots, scatter plots, and normal probability plots, can provide alternative views of the cancer statistics. These can also display supporting statistics such as error, confidence intervals, distributions, sample or population sizes, and standard deviation.
